Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-03 ms/main.tex
formatting

%\begin{enumerate} % p* version
%\item Fixation of cooperation,
%	if $T_A>T_B$ and $0<\tilde{p}^*$, or
%	if $T_A>T_B$ and $0<\tilde{p}^*<1$, and $\tilde{p}_0>\tilde{p}^*$, or
%	if $T_A<T_B$ and $1<\tilde{p}^*$.
%\item Global fixation of defection,
%	if $T_A>T_B$ and $\tilde{p}^*>1$, or
%	if $T_A>T_B$ and $0<\tilde{p}^*<1$, and $\tilde{p}_0<\tilde{p}^*$, or
%	if $T_A<T_B$ and $\tilde{p}^*<0$
%\item Co-existence of both phenotypes at $\tilde{p}^*$, 
%	if $T_A<T_B$ and $0<\tilde{p}^*<1$.
%\end{enumerate}
\begin{enumerate} % gamma version
\item \emph{Fixation of cooperation}:
	if \emph{(i)} $T=T_A=T_B$ and $c < b \cdot \alpha \frac{T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c<\gamma_1$; or
	if \emph{(iii)} $T_A<T_B$ and $c<\gamma_2$.
\item \emph{Fixation of defection}:
	if \emph{(iv)} $T=T_A=T_B$ and $c > b \cdot \alpha \frac{T}{1-T}$; or
	if \emph{(vi)} $T_A>T_B$ and $\gamma_2<c$; or
	if \emph{(vi)} $T_A<T_B$ and $\gamma_1<c$.
\item \emph{Fixation of either phenotype depending on initial frequency}: 
	if \emph{(vii)} $T_A>T_B$ and $\gamma_1<c<\gamma_2$.
\item \emph{Coexistence of both phenotypes at $\tilde{p}^*$}:
	if \emph{(viii)} $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
\end{enumerate}
\end{result}

@@

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
\item \emph{Fixation of the defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_2 < c$ and $\hat\gamma_1 < c$; or 
	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $\hat\gamma_1 < c$ and $\hat\gamma_2 > c$; or
  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
\item \emph{Fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_1< c < \hat\gamma_2$.
\end{enumerate}

@@

% Javarone MA, Atzeni AE, Galam S. Emergence of Cooperation in the Prisoner ’ s Dilemma Driven by Conformity. 2:155-163. doi:10.1007/978-3-319-16549-3
% Woodcock S. The significance of non-vertical transmission of phenotype for the evolution of altruism. Biol Philos. 2006;21:213-234. doi:10.1007/s10539-005-8241-1

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
% Acknowledgements
{\small
\section*{Acknowledgements}
We thank Lilach Hadany and Ayelet Shavit for discussions and comments.
This work was supported in part by
the Israel Science Foundation 552/19 (YR),
and Minerva Stiftung Center for Lab Evolution (YR).
% TODO funding for other authors?
}

>>>>

%\begin{enumerate} % p* version
%\item Fixation of cooperation,
%	if $T_A>T_B$ and $0<\tilde{p}^*$, or
%	if $T_A>T_B$ and $0<\tilde{p}^*<1$, and $\tilde{p}_0>\tilde{p}^*$, or
%	if $T_A<T_B$ and $1<\tilde{p}^*$.
%\item Global fixation of defection,
%	if $T_A>T_B$ and $\tilde{p}^*>1$, or
%	if $T_A>T_B$ and $0<\tilde{p}^*<1$, and $\tilde{p}_0<\tilde{p}^*$, or
%	if $T_A<T_B$ and $\tilde{p}^*<0$
%\item Co-existence of both phenotypes at $\tilde{p}^*$, 
%	if $T_A<T_B$ and $0<\tilde{p}^*<1$.
%\end{enumerate}
\begin{enumerate} % gamma version
\item \emph{Fixation of cooperation}:
	if \emph{(i)} $T=T_A=T_B$ and $c < b \cdot \alpha \frac{T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c<\gamma_1$; or
	if \emph{(iii)} $T_A<T_B$ and $c<\gamma_2$.
\item \emph{Fixation of defection}:
	if \emph{(iv)} $T=T_A=T_B$ and $c > b \cdot \alpha \frac{T}{1-T}$; or
	if \emph{(v)} $T_A>T_B$ and $\gamma_2<c$; or
	if \emph{(vi)} $T_A<T_B$ and $\gamma_1<c$.
\item \emph{Stable coexistence of both phenotypes at $\tilde{p}^*$}:
	if \emph{(vii)} $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
\item \emph{Unstable coexistence and fixation of either phenotype depending on initial frequency}: 
	if \emph{(viii)} $T_A>T_B$ and $\gamma_1<c<\gamma_2$.
\end{enumerate}
\end{result}

@@

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iii.a)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iii.b)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
\item \emph{Fixation of defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_1 < c$ and $\hat\gamma_2 < c$; or 
	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
\item \emph{Stable Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(vii.a)} $T_A < T_B$ and $v<\hat{v}$ and $\hat\gamma_1 < c < \hat\gamma_2$; or
  if \emph{(vii.b)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
\item \emph{Unstable coexistence and fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
\end{enumerate}

@@

% Javarone MA, Atzeni AE, Galam S. Emergence of Cooperation in the Prisoner ’ s Dilemma Driven by Conformity. 2:155-163. doi:10.1007/978-3-319-16549-3

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \pagebreak
% Acknowledgements
{\small
\section*{Acknowledgements}
We thank Lilach Hadany and Ayelet Shavit for discussions and comments.
This work was supported in part by
the Israel Science Foundation 552/19 (YR),
and Minerva Stiftung Center for Lab Evolution (YR).
% TODO funding for other authors?
}
